Combine_results

### 2017-04-16 Code/3_combine_results.Rmd
move reorder as map to step3

```{r add_Census_Variables, echo = F}
BlackWhite_results <- add_Census_Region(BlackWhite_results, state)
BlackWhite_results <- add_Census_Division(BlackWhite_results, state)
BlackWhite_results$stabbrs <- state.abb[match(BlackWhite_results$state, state.name)]
BlackWhite_results$stabbrs[BlackWhite_results$state == "Washington DC"] <- "DC"

cod_decomp_results <- merge(BlackWhite_results %>% select(stratum.id, Census_Region, Census_Division, stabbrs), 
                            cod_decomp_results, by = "stratum.id", all.y = T)
```

>>>>

```{r add_Census_Variables, echo = F}
BlackWhite_results <- add_Census_Region(BlackWhite_results, state)
BlackWhite_results <- add_Census_Division(BlackWhite_results, state)
BlackWhite_results <- reorder.as.map(BlackWhite_results, "state", "stabbrs")

BlackWhite_results$stabbrs <- state.abb[match(BlackWhite_results$state, state.name)]
BlackWhite_results$stabbrs[BlackWhite_results$state == "Washington DC"] <- "DC"

cod_decomp_results <- merge(BlackWhite_results %>% select(stratum.id, Census_Region, Census_Division, stabbrs), 
                            cod_decomp_results, by = "stratum.id", all.y = T)
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")

```
